\documentclass[a4paper]{article}
    \usepackage{hyperref}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=5in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.4in,right=0.4in,bottom=0.3in,top=0.5in]{geometry}
\usepackage{etoolbox,refcount}
\usepackage{multicol}


\newcounter{countitems}
\newcounter{nextitemizecount}
\newcommand{\setupcountitems}{%
  \stepcounter{nextitemizecount}%
  \setcounter{countitems}{0}%
  \preto\item{\stepcounter{countitems}}%
}
\makeatletter
\newcommand{\computecountitems}{%
  \edef\@currentlabel{\number\c@countitems}%
  \label{countitems@\number\numexpr\value{nextitemizecount}-1\relax}%
}
\newcommand{\nextitemizecount}{%
  \getrefnumber{countitems@\number\c@nextitemizecount}%
}
\newcommand{\previtemizecount}{%
  \getrefnumber{countitems@\number\numexpr\value{nextitemizecount}-1\relax}%
}
\makeatother    
\newenvironment{AutoMultiColItemize}{%
\ifnumcomp{\nextitemizecount}{>}{3}{\begin{multicols}{2}}{}%
\setupcountitems\begin{itemize}}%
{\end{itemize}%
\unskip\computecountitems\ifnumcomp{\previtemizecount}{>}{3}{\end{multicols}}{}}


    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.7ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=black,
    pdftitle={Eishkaran's Resume},
    pdfpagemode=FullScreen,
    }

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2 
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-9pt}
\begin{center}
	{\Huge \scshape {Eishkaran Singh}}\\
	\vspace{1mm}
	India $\cdot$ \underline{eishkaransingh@gmail.com} $\cdot$ +91 7087694506 $\cdot$ \href{https://github.com/EISHKARAN}{\underline{Github}} $\cdot$ \href{https://www.linkedin.com/in/eishkaran-singh/}{\underline{Linkedin}} \\
\end{center}
%==== Education ====%
\vspace{-2mm}
\header{Education}
\vspace{0.5mm}
\textbf{Thapar Institute of Engineering and Technology}\hfill Patiala\\
BTech Computer  Engineering \hfill September 2021 - Present\\
\vspace{0.5mm}
\textbf{Indian Institute of Technology}\hfill Madras\\
Bs Data Science and Applications \hfill January 2022 - Present\\
\vspace{-0.5mm}
\header{Publications}
\vspace{-0.5mm}
\textbf{GlucoBreath: Non-Invasive Glucometer to Detect Diabetes using Breath}
    {\textit{Ritu Kapur, Yashwant Kumar, Swati Sharma, Shivani, Eishkaran Singh, Dhruv Rohilla, Bhupinder Kumar, Vikrant Kanwar, Arnav Bhavsar, and Varun Dutt}}\\
\vspace{0.5 mm}
Pre-Print Link:https: \url{https://doi.org/10.36227/techrxiv.24448963.v1} \\
Under Review IEEE Sensors Journal\\
% \vspace{0.5 mm}
% \textbf{AIM-CVT: Design of a Framework for the AI-Enabled-Multilingual Court Verdict Translator}
%     {\textit{Eishkaran Singh, Sachin Kansal, Arshjot Singh}}\\
% \vspace{0.5 mm}
% Submission Id:- EVOS-D-23-00559\\
% Under Review Evolving Systems Journal\\
\vspace{-0.5 mm}
\header{Experience}
\vspace{-1mm}
{\textbf{Columbia University}}\hfill November 2023 - Present \\
 {\textit{Research Intern under Prof. (Dr.)Eugene Wu }}  \
\vspace{-2mm}
\begin{itemize} 
\item Pioneering the development of automation methodologies for Kaggle competitions through the strategic integration of Large Language Models, optimizing processes for heightened efficiency and competitive advantage.
\end{itemize}
\vspace{-1.5mm}
{\textbf{Carneige Mellon University}}\hfill November 2023 - Present \\
 {\textit{Research Intern under Prof. (Dr.)Min Xu at XuLabs}}  \
\vspace{-2mm}
\begin{itemize} 
\item Currently engaged in cutting-edge research in biomedical image analysis, with a focus on the application of cryo-electron tomography (cryo-ET) and cryo-electron microscopy (cryo-EM) techniques for advanced image processing and analysis.
\end{itemize}
\vspace{-2mm}
{\textbf{Indian Institute of Technology Indore}}\hfill July 2023 - Present \\
 {\textit{Research Intern under Prof. (Dr.)Chandresh Kumar Maurya }}  \
\vspace{-2mm}
\begin{itemize} 
\item Proficiently contributed to the alignment of diverse text-to-text and text-to-audio scripts across 14 distinct Indian languages, employing a range of advanced aligner tools.  
\vspace{-2.5mm}
\item Employed NLP and IndicNLP libraries for text preprocessing, constructing a gold standard dataset to drive the application of various ML/DL models.
\end{itemize}
\vspace{-1.5mm}
{\textbf{Indian Institute of Technology Mandi}}\hfill June 2023 - Present \\
 {\textit{Research Intern under Prof. (Dr.)Varun Dutt in Digital Nose Project}}  \
\vspace{-2mm}
\begin{itemize} 
\item Orchestrated migration of local workflows to servers using automation and DevOps principles, optimizing operational efficiency and boosting machine learning model accuracy. 
\vspace{-2mm}
\item Utilized FastAPI to create asynchronous functions for process automation and applied machine learning algorithms, including classification and stack meta-modeling, to boost predictive accuracy.
\end{itemize}
\vspace{-2mm}
{\textbf{Thapar Institute of Engineering and Technology}}\hfill May 2023 - Present \\
 {\textit{Research Intern under Prof. (Dr.) Sachin Kansal }}  \
\vspace{-2mm}
\begin{itemize} 
\item Developed an efficient pipeline for extracting frames from video data, utilising advanced image processing techniques, parallel processing, and error handling. 
\vspace{-2mm}
\item Optimised the pipeline's performance, enabling swift extraction of frames from large-scale video datasets while ensuring accuracy and data integrity.
\vspace{-2mm}
\item Leveraged Beautiful Soup and bs4 libraries to surpass Google Translate's 5000-character limit, enabling translation of unlimited text seamlessly.
\end{itemize}
\vspace{-2mm}
{\textbf{Thapar Institute of Engineering and Technology}}\hfill June 2023-July 2023 \\
 {\textit{Guest Lecturer}}  \
\vspace{-2mm}
\begin{itemize} 
\item Invited as guest of  honour to deliver the lecture in Thapar summer School of Machine learning and deep Learning and delivered 6 lectures on Image Processing and natural language processing.
\end{itemize}
\vspace{-1.5mm}
\header{Projects/Achievements}
{\textbf{PixelMind AI}} \hfill May 2023 \\
\vspace{-3mm}
\begin{itemize} 
	\item Paradox’23 in Indian Institute of Technology Madras organised a contest in thhe domain of Image enhancement for students and industry professionals where I won 2nd Position and won a cash Prize of Rs.50K.
    \vspace{-2mm}
    \item Utilized a combination of C language and Python, along with image processing funcitons, to significantly expedite image enhancement compared to competitors in a time-efficient manner.
\end{itemize}
\vspace{-2.5mm}
{\textbf{Kaggle Master}} \hfill June 2023 \\
\vspace{-1mm}
\url{https://www.kaggle.com/eishkaran} \\
\vspace{-1.5mm}
\begin{itemize} 
    \vspace{-1mm}
    \item Participated in a global Kaggle competition on Binary Classification with Software Defects, competing against 1702 teams worldwide. Achieved an impressive world ranking of 44, placing in the top 3\% of participants. Employed advanced classifier models to optimize accuracy within the shortest time frame, demonstrating a strong commitment to efficiency and excellence in data analysis and predictive modeling
\vspace{-2.5mm}
\end{itemize}
\vspace{-2mm}
\header{Skills}
\vspace{0.5mm}
\begin{tabular}{ l l }
	Programming Languages: & Python, C++ ,C  \\
	Database Management Systems: & MySQL , Oracle \\ 
    Cloud Computing: & GCP, AWS\\
	Web Development:       & HTML , CSS, JavaScript   \\
    Tech Stack:       & Flask , FastAPI   \\
	Libraries / Frameworks: & Pandas, Numpy, Seaborn, Tensorflow, Pytorch, XGBoost, scikit-learn, OpenCv, PIL       \\
	Machine Learning:             & Regression, Classification, Clustering, Neural Networks, Deep Learning, LLM\\
	Soft Skills:           &  Public Speaking, Leadership  \\
	
\end{tabular}


% \vspace{0.5mm}
% \header{MISCELLANEOUS}
% {\textbf{Career Certificates }} \hfill Jan 2023\\  \\Python, MySQL, Pandas, Supervised Machine Learning, Advanced Algorithms\\ 
% {\textbf{Silver Zone Olympiad }} \hfill September 2020\\  \\International Informatics Olympiad\\ 
\end{document}
